---
title: "Challenge-4"
author: "Insert your name here"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
p.comment {
background-color: #DBDBDB;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}

</style>

## Questions
<br>

Load the "comm_data.csv" dataset using the `read_csv()` command and assign it to a variable named "comm_data." 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data <- read.csv("comm_data.csv")
```
<br>


#### Question-1: Communication Chronicles

Using the select command, create a new dataframe containing only the "date," "channel," and "message" columns from the "comm_data" dataset.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(dplyr)
selected_data1 <- comm_data %>%
  select(date, channel, message)
```
<br>

#### Question-2: Channel Selection

Use the filter command to create a new dataframe that includes messages sent through the "Twitter" channel on August 2nd.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
selected_data2 <- comm_data %>%
filter(channel == "Twitter", date == as.Date("2023-08-02"))
```
<br>

#### Question-3: Chronological Order

Utilizing the arrange command, arrange the "comm_data" dataframe in ascending order based on the "date" column.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
sorted_data <- arrange(comm_data, date)
```
<br>

#### Question-4: Distinct Discovery

Apply the distinct command to find the unique senders in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
unique_senders <- distinct(comm_data, sender)
```
<br>

#### Question-5: Sender Stats

Employ the count and group_by commands to generate a summary table that shows the count of messages sent by each sender in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
summary_table1 <- comm_data %>%
  group_by(sender) %>%
  summarise(message_count = n())
summary_table1
```
<br>

#### Question-6: Channel Chatter Insights

Using the group_by and count commands, create a summary table that displays the count of messages sent through each communication channel in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
summary_table2 <- comm_data %>%
  group_by(channel) %>%
  count()
summary_table2
```
<br>

#### Question-7: Positive Pioneers

Utilize the filter, select, and arrange commands to identify the top three senders with the highest average positive sentiment scores. Display their usernames and corresponding sentiment averages.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
filtered_data <- comm_data %>%
  filter(sentiment > 0)
summary_table <- filtered_data %>%
  group_by(sender) %>%
  summarise(avg_sentiment = mean(sentiment))
sorted_summary_table <- summary_table %>%
  arrange(desc(avg_sentiment))
top_three_senders <- sorted_summary_table %>%
  head(3)
select(top_three_senders, sender, avg_sentiment)

```
<br>

#### Question-8: Message Mood Over Time

With the group_by, summarise, and arrange commands, calculate the average sentiment score for each day in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
summary_table <- comm_data %>%
  group_by(date) %>%
  summarise(avg_sentiment = mean(sentiment))
sorted_summary_table <- summary_table %>%
  arrange(date)
```
<br>

#### Question-9: Selective Sentiments

Use the filter and select commands to extract messages with a negative sentiment score (less than 0) and create a new dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
negative_sentiment_data <- comm_data %>%
  filter(sentiment < 0)
negative_sentiment_data <- negative_sentiment_data %>%
  select(date, sender, message)
```
<br>

#### Question-10: Enhancing Engagement

Apply the mutate command to add a new column to the "comm_data" dataframe, representing a sentiment label: "Positive," "Neutral," or "Negative," based on the sentiment score.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data <- comm_data %>%
  mutate(sentiment_label = ifelse(sentiment > 0, "Positive",
             ifelse(sentiment == 0, "Neutral", "Negative")))
comm_data
```
<br>

#### Question-11: Message Impact

Create a new dataframe using the mutate and arrange commands that calculates the product of the sentiment score and the length of each message. Arrange the results in descending order.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
new_data <- comm_data %>%
  mutate(sentiment_length_product = sentiment * nchar(message))
sorted_data <- new_data %>%
  arrange(desc(sentiment_length_product))
```
<br>

#### Question-12: Daily Message Challenge

Use the group_by, summarise, and arrange commands to find the day with the highest total number of characters sent across all messages in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
char_count_by_day <- comm_data %>%
  group_by(date) %>%
  summarise(total_chars_sent = sum(nchar(message)))
sorted_char_count <- char_count_by_day %>%
  arrange(desc(total_chars_sent))
day_with_highest_chars <- sorted_char_count[1, ]
day_with_highest_chars
```
<br>

#### Question-13: Untidy data

Can you list at least two reasons why the dataset illustrated in slide 10 is non-tidy? How can it be made Tidy?

**Solution:** _Messy columns, missing data etc. all can lead to a need of reshaping of untidy dataset. pivot_longer from dplyr is an effective tool to rectify it._